Fixing Vulnerabilities Hinders Maintainability

### 2019-05-07 paper/ICPC19/icpc19.tex
table structure

\begin{table}[h]
	\caption{Guidelines to produce maintainable code}
\begin{tabular}{L{2.5cm}L{5.5cm}}

\toprule
\textbf{10 Guidelines} & \textbf{Description}\\
\midrule
\textbf{Write Short Units of Code} & Limit code units to $15$ LOCs because smaller
 units are easier to understand, reuse and test them\\\midrule
\textbf{Write Simple Units of Code} & Limit branch points to $4$ per unit because
it makes units easier to test and modify \\\midrule
\textbf{Write Code Once} & Do not copy code because bugs tend to replicate at
multiple places (inefficient and error-prone)\\\midrule
\textbf{Keep Unit Interfaces Small} & Limit the number of parameters to at most
$4$ because it makes units easier to understand and reuse\\\midrule
\textbf{Separate Concerns in Modules} & Avoid large modules because changes in
loosely coupled databases are easier to oversee and execute\\\midrule
\textbf{Couple Architecture Components Loosely} & Minimize the amount of code
within modules that are exposed to modules in other components\\\midrule
\textbf{Keep Architecture Components Balanced} & Balancing the number of
components ease locating code and allow for isolated maintenance\\\midrule
\textbf{Keep your Codebase Small} & Reduce and avoid the system size because
small products are easier to manage and maintain\\\midrule
\textbf{Automate Tests} & Test your codebase because it makes development
predictable and less risky\\\midrule
\textbf{Write Clean Code} & Avoid producing software with code smells because
it is more likely to be maintainable in the future\\
\bottomrule
\end{tabular}
\label{tab:guidelines}
\end{table}

>>>>

\begin{table}[h]
	\caption{Guidelines to produce maintainable code}
\begin{tabular}{L{2cm}L{4cm}L{1cm}}

\toprule
\textbf{10 Guidelines} & \textbf{Description} & \textbf{Metric}\\
\midrule
\textbf{Write Short Units of Code} & Limit code units to $15$ LOCs because smaller
 units are easier to understand, reuse and test them & \\\midrule
\textbf{Write Simple Units of Code} & Limit branch points to $4$ per unit because
it makes units easier to test and modify & \\\midrule
\textbf{Write Code Once} & Do not copy code because bugs tend to replicate at
multiple places (inefficient and error-prone) &\\\midrule
\textbf{Keep Unit Interfaces Small} & Limit the number of parameters to at most
$4$ because it makes units easier to understand and reuse & \\\midrule
\textbf{Separate Concerns in Modules} & Avoid large modules because changes in
loosely coupled databases are easier to oversee and execute & \\\midrule
\textbf{Couple Architecture Components Loosely} & Minimize the amount of code
within modules that are exposed to modules in other components & \\\midrule
\textbf{Keep Architecture Components Balanced} & Balancing the number of
components ease locating code and allow for isolated maintenance & \\\midrule
\textbf{Keep your Codebase Small} & Reduce and avoid the system size because
small products are easier to manage and maintain & \\\midrule
\textbf{Automate Tests} & Test your codebase because it makes development
predictable and less risky & \\\midrule
\textbf{Write Clean Code} & Avoid producing software with code smells because
it is more likely to be maintainable in the future & \\
\bottomrule
\end{tabular}
\label{tab:guidelines}
\end{table}
